Graph Generators for Data Science: A Survey

### 2018-07-11 data_sets.tex
Some changes to datasets section and bibliography

\paragraph{Information Diffussion}
% - http://pure-oai.bham.ac.uk/ws/files/14790571/srep02980.pdf
% - https://www.americanvoiceforfreedom.org/wp-content/uploads/2018/03/The-spread-of-true-and-false-news-online.pdf

 \paragraph{Knowledge bases}
% - Wikipedia https://en.wikipedia.org/wiki/Wikipedia:Database_download

>>>>

\paragraph{Information Diffussion}

Information networks are studied using graph algorithms in order to understand
how information propagates. As such, there several datasets used to understand
such networks.

\begin{itemize}
  \item Higgs-Twitter~\cite{de2013anatomy}: This dataset contains the Twitter
    network before, during and after the discovery of the Higgs boson.
    Concretely, it contains the tweets, the mentions, retweets,
    followers/followees, etc.  
  \item Memetracker~\cite{leskovec2009memede2013}: Memetracker is a dataset that
    contains the quotes and phrases that appear more frequently on the entire
    news spectrum. It consists of the links of the news, the time and memes, and
    is used to understand how information spanws, evolves and dies.
\end{itemize}

 \paragraph{Semantic Web and Knowledge bases}

% - Wikipedia https://en.wikipedia.org/wiki/Wikipedia:Database_download
% - DbPedia
